*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-07 Code/Manuscript_O2.Rmd
minor edits
fixed a citation

*Prochlorococcus marinus* clades are nonetheless found in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulationsStratified1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy regions in OMZ at depths shallower than 40 m [@lavinNovelLineagesProchlorococcus2010], exploiting ambient light levels above what LL clades were thought to tolerate.

@@

Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA Maine, USA. MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLII/III) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade. Cultures were maintained in incubators set to 22°C with a light/dark cycle of 12 h. The PAR level for maintenance cultures reflected PAR in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were transferred weekly with 1 in 5 dilutions with Pro99 media [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial seawater [@bergesEvolutionArtificialSeawater2001].

>>>>

*Prochlorococcus marinus* clades are nonetheless found in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulations1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy regions in OMZ at depths shallower than 40 m [@lavinNovelLineagesProchlorococcus2010], exploiting ambient light levels above what LL clades were thought to tolerate.

@@

Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA Maine, USA. MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLII/III) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade. Cultures were maintained in incubators set to 22°C with an on/off light/dark cycle of 12 h. The PAR level for maintenance cultures reflected PAR in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were transferred weekly with 1 in 5 dilutions with Pro99 media [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial seawater [@bergesEvolutionArtificialSeawater2001].
